A fully labelled proof system for intuitionistic modal logics

### 2020-09-30 FullyLabelled/JLC/introduction.tex

Besides that, there is another pleasant observation to make about our
system. It is naturally a multi-conclusion system. Ordinary labelled sequent systems for intuitionistic modal
logic are single-conclusion~\cite{simpson:phd}. 
%
The same is true for the corresponding nested sequent
systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
Maehara style multi-conclusion systems in nested
sequents~\cite{str:2017maehara}, and therefore also in ordinary
labelled sequents. However, also in these systems there are rules
($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
premise, even though this is not the case in labelled
systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83}\lutz{wrong ref} for
intuitionistic logic.

>>>>

Besides that, there is another pleasant observation to make about our
system. It is naturally a multi-conclusion system. Ordinary labelled sequent systems for intuitionistic modal
logic are single-conclusion~\cite{simpson:phd}. 
%
The same is true for the corresponding nested sequent
systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
Maehara style multi-conclusion systems in nested
sequents~\cite{str:2017maehara}, and therefore also in ordinary
labelled sequents. However, also in these systems there are rules
($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
premise, even though this is not the case in labelled
systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:2014} for
intuitionistic logic.
